---
author: "`r Sys.info()[length(Sys.info())-1]`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    html_document:
        fig_caption: yes
title: "`r paste0('CSAW differential binding stats report')`"
---

```{r setup, include=FALSE}
# .libPaths(R.home("library"))

knitr::opts_chunk$set(echo = FALSE)
```

```{r}
## snakemake@params[["fdr"]]
FDR <- 0.5## I know this is crazy
## snakemake@params[["lfc"]]
LFC <- 1
```

### Overview

This report summarizes statistical analysis of binding events using group information provided in sample sheet 

### Analysis input

```{r data_load}
## DBdata<-file.path(snakemake@params[["outdir"]], "DiffBinding_analysis.Rdata")
DBdata <- '/home/imallona/cenp_chip/mapping/CSAW_MACS2_conditions/DiffBinding_analysis.Rdata'
## useSpikeInForNorm<-snakemake@params[["useSpikeInForNorm"]]
useSpikeInForNorm <- FALSE

suppressMessages(require(GenomicRanges))
suppressMessages(require(csaw))
load(DBdata)
```

### Statistical analysis

Statistical model was fit according to the following design:

```{r design_used}
chip_object$design
```

The original windows were merged into `r length(chip_results$mergedRegions$region)` regions, for which p values were combined and FDR estimates were obtained after adjustment for multiple testing.
The absolute log fold change of the window with the smallest p value belonging to a merged region was reported as best log fold change for that region.


### Unfiltered results

```{r filter_results}
merged <- chip_results$mergedRegions
tabcom <- chip_results$combinedPvalues
merged$region$score <- -10 * log10(tabcom$FDR)
names(merged$region) <- paste0("region", 1:length(merged$region))
tabcom$name <- names(merged$region)
tabx <- as.data.frame(merged$region, stringsAsFactors=FALSE)
tabx$name <- rownames(tabx)
full_res <- as.data.frame(merge(x=tabx, y=tabcom, by.x="name", by.y="name"), stringsAsFactors=FALSE)
```

How is the pvalue distribution?

```{r}
hist(full_res$PValue)
```

How many do have an unadjusted pval < 0.05?

```{r}
print(full_res[full_res$PValue < 0.05,])
table(full_res[full_res$PValue < 0.05,'direction'])
```

Yet these are inusual, e.g. not uniform http://varianceexplained.org/statistics/interpreting-pvalue-histogram/ , maybe we could correct with https://www.huber.embl.de/users/klaus/Teaching/DESeq2Predoc2014.html#inspection-and-correction-of-pvalues , e.g. “empirical null modelling”


```{r, fig.height = 10, fig.width = 8}
library(fdrtool)

head(full_res)

new_fdr <- fdrtool(full_res$PValue, statistic = "pvalue", plot = TRUE)
summary(new_fdr$qval)

## these are not zscores but
hist(scale(full_res$best.logFC))
another_fdr <- fdrtool(as.numeric(scale(full_res$best.logFC)), statistic = "normal", plot = TRUE)
summary(another_fdr$qval)
```

### Filtering of results


```{r}
fdrcutoff <- as.numeric(FDR)
lfccutoff <- as.numeric(LFC)
full_res.filt <- subset(full_res, (FDR<=fdrcutoff) & (abs(best.logFC) >= lfccutoff))
```


```{r direction_list}
table(full_res.filt$direction)
```
